Extreme Value Chapter 3

### 2022-03-01 Ch3_samplesize/Figures_Ch3.Rmd
Working on Figure 4

```{r fig.width=4, fig.height=2.5}
nreps_mles_df %>% 
  ggplot()+
  geom_point(aes(x = alpha_star, y = k_star, color = "Simple Lomax"), size = 4, alpha = 0.5) +
  geom_point(aes(x = alpha_glm, y = k_glm, color = "Lomax GLM"), size = 4, alpha = 0.5) +
  scale_y_log10() +
  scale_x_log10() +
  scale_color_manual(values = c("grey20", "dodgerblue4"), name = "") +
  labs(x = "Log(alpha)", y = "Log(k)") +
  theme_bw() +
  theme(legend.position = "bottom") -> a

@@

top <- plot_grid(a + theme(legend.position = "none"), b, ncol = 2)

plot_grid(top, ableg, nrow = 2, rel_heights = c(1, 0.1))

@@

Do MSE? or bias to show that the are biased estimators:

```{r fig.height=2.5, fig.width=5}
nreps_mles_df %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  group_by(thresh_tests, samp_n_tests) %>% 
  summarize(Eval_theta_hat = mean(log_St_hat2),
            theta = mean(theta),
            bias = Eval_theta_hat - theta) %>% 
  ggplot(., aes(y = bias, x = thresh_tests)) +
  geom_jitter(aes(color = samp_n_tests), size = 3, alpha = 0.9, width = 0.1) +
  geom_hline(yintercept = 0, color = "grey") +
  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
  labs(x = "Distance level", y = "Bias", subtitle = "GLM Lomax") +
  theme_bw()

@@

# Figure 5
Bias correction

>>>>

```{r fig.width=6, fig.height=3}
nreps_mles_df %>% 
  ggplot()+
  geom_point(aes(x = alpha_star, y = k_star, color = "Simple Lomax"), size = 4, alpha = 0.5) +
  geom_point(aes(x = alpha_glm, y = k_glm, color = "Lomax GLM"), size = 4, alpha = 0.5) +
  scale_y_log10() +
  scale_x_log10() +
  scale_color_manual(values = c("grey20", "dodgerblue4"), name = "") +
  labs(x = "Log(alpha)", y = "Log(k)") +
  theme_bw() +
  theme(legend.position = "bottom") -> a

@@

top <- plot_grid(a + theme(legend.position = "none"), b, ncol = 2, labels = "AUTO", label_size = 8)

plot_grid(top, ableg, nrow = 2, rel_heights = c(1, 0.1))
ggsave("Ch3_samplesize/Figures/Figure3.png")

@@

Bias correction in GLM Lomax

```{r eval = FALSE, fig.height=2.5, fig.width=5}
nreps_mles_df %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  group_by(thresh_tests, samp_n_tests) %>% 
  summarize(Eval_theta_hat = mean(log_St_hat2),
            theta = mean(theta),
            bias = Eval_theta_hat - theta) %>% 
  ggplot(., aes(y = bias, x = thresh_tests)) +
  geom_jitter(aes(color = samp_n_tests), size = 3, alpha = 0.9, width = 0.1) +
  geom_hline(yintercept = 0, color = "grey") +
  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
  labs(x = "Distance level", y = "Bias", subtitle = "GLM Lomax") +
  theme_bw()

@@
